# Homework for week 4

## Reproduce

### package versions

```{r first, eval=FALSE}
# a snapshot have been taken
# renv::snapshot()

#install the same packages
#renv::restore()
```

* The library is already synchronised with the lockfile

### Read in data:

Located within the data folder:

* HDI data from: http://hdr.undp.org/en/indicators/68606#
* Shapefile from: https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-2.688200%2C0.000000%2C1.41

## Load packages
```{r}
library(sf)
library(tidyverse)
library(janitor)
library(readr)
library(here)
library(countrycode)
```

## Read data
```{r}
shape <- st_read(here("data","World_Countries_(Generalized)","World_Countries__Generalized_.shp"))

csv <- read_csv(here("data","Gender Inequality Index (GII).csv"), 
                     locale = locale(encoding = "latin1"),
                     na = "..", skip = 5)
```
## Select data

Creating a new column of difference in inequality between 2010 and 2019, and change country name to country code, using the 'countrycode' package

```{r}
csv_diff <- csv%>%
  clean_names()%>%
  select(country,x2010,x2019)%>%
  mutate(diff_gender =x2010-x2019) %>%
  slice(1:189,)%>%
  mutate(iso_code=countrycode(country, origin='country.name',destination = 'iso2c'))

```

## Join

Join the new column of difference in inequality between 2010 and 2019 to spatial data of the World

```{r}
joined_data <- shape %>% 
  clean_names() %>%
  left_join(., 
            csv_diff,
            by = c("aff_iso"= "iso_code"))

```

